**Machine learning identifies unique taxa differentiating proximal and distal

### 2017-05-15 submission/manuscript.Rmd
manuscript

Similarly, when examining community structure between sites and sides, there is no clear pattern among individuals. Microbial communities do not separate on an ordination by the left or right sides in either the mucosal or lumenal samples (Figure 2C).

>>>>

To determine if the structure of the community is consistent between locations we constructed an NMDS ordination to examine the distances between each sample. We found that microbial communities do not cluster on an ordination by the left or right sides in either the mucosal or lumenal samples (Figure 2C). Previous human microbiome studies that have sampled multiple sites have found that individuals are typically more similar to themselves than others in the study (cite). To see if this effect was driving the organization of the ordination, we connected communities from the same individual using gray lines on Figure 2C. While some individuals did have samples that clustered near each other (shorter lines), there were just as many individuals who's samples diverged from each other (longer lines). Similar to the diversity metrics, when examining community structure between sites and sides, there is no clear pattern between or within individuals.
